What's in a Name? Linear Temporal Logic Literally Represents Time Lines

### 2023-01-02 paper/main.tex
added realworld tests

\usepackage{amsmath, amssymb, amsthm,tikz}
\usetikzlibrary{positioning,shapes,quotes,calc}

@@

KYR: Here we nicely show (with pictures as much as possible) all of the individual statistics and results we gathered (note aggregation occurs below).

>>>>

\usepackage{amsmath, amssymb, amsthm,tikz, subfig}
\usetikzlibrary{positioning,shapes,quotes,calc}

@@

KYR: Here we nicely show (with pictures as much as possible) all of the individual statistics and results we gathered (note aggregation occurs below).
\paragraph{Real-world datasets} We study the feasibility of our tool on a benchmark suite of LTL formulas gathered from real world use cases.

We gather a test suite of 91 formulas used in real-world requirement specification. We take $6$ specifications from NASA's Automated Airspace Concept (AAC)\cite{GCMTR16}. We also collect formulas from the Acacia suite of examples \cite{RV10}. We reap $85$ formulas from the suit of $23$ examples, by generating seperate visualizations for each line of specification. % We choose to visualize each formula specifically, rather than complete specifications, as

We run \texttt{ltl2regex} on these $91$ examples, the tool completes execution (within timeout of $20$s) on $87$. Within the $87$, two examples have regular expressions of star height $8$ and are intractible to generate graph visualizations of. We are able to generate tractible visualization on the $85$, or over $93\%$ of benchmarks tested. The plots of visualization complexity on these formula are provided below in \cref{fig:real-world}.

\begin{figure}[h!]
    \centering
    \subfloat{{\includegraphics[width=6.5cm]{img/naive-ltl2tl-scatterplot-omit-big-values.png} }}%
    \quad % [\centering label 1]
    \subfloat{{\includegraphics[width=6.5cm]{img/star-height-scatter-plot.png}}}
    \caption{Visualization complexity metrics for formulas collected from Acacia \cite{RV10} and NASA's  AAC \cite{GCMTR16}}
    \label{fig:real-world}
\end{figure}
